Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-05-13 doc/main_jfm.tex
figures changed

\begin{figure}
\centering
\includegraphics[width=0.22\textwidth]{N116_ext_0.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_2500.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_5000.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_7500.eps}\\
\includegraphics[width=0.22\textwidth]{N116_shear_3000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_6000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_9000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_12000.eps}
  \caption{Two vesicles under a linear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a) and two sets of simulation results are two vesicles under: 
  (b)-(d) extensional flow and (e)-(h) shear flow. 
  }
    \label{figure5}
\end{figure}

Figure~\ref{figure5} shows two sets of simulations. Starting from the initial configuration (shown in panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow. The flow is stretching along the $y$ direction and squeezing in $x$ direction. Hence two vesicles are first pushed toward each other  then separate along the streamline. With the same starting state, panels (e)-(h) are the observed phenomena when two vesicles are in a shear flow $\dot x = \dot\gamma y$. An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned. One can notice that the starting 
state of two vesicles are both centered on the x-axis. If two center of mass positions are not at the same horizontal level, then the adhesion observed in the shear flow case will be absent when they are well separated in $y$-direction.

@@

\begin{equation}
{\bf v}_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2 \right]{\bf e}_x,
\end{equation}
%
where $v_{max}$ is the flow strength and $w$ controls the shape of the flow. $R_0$ is defined as the radius of the initial vesicle midplane. Figure~\ref{figure6} gives a final configuration for one specific case where the circular vesicle is initially placed above the $x$-axis.

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{N58_parabolic.eps}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=20000$.
  }
    \label{figure6}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.22\textwidth]{N116_ext_0.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_2500.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_5000.eps}
\includegraphics[width=0.22\textwidth]{N116_ext_7500.eps}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a).
  }
    \label{figure5}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.22\textwidth]{N116_ext_0.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_3000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_6000.eps}
\includegraphics[width=0.22\textwidth]{N116_shear_9000.eps}
  \caption{Two vesicles under a shear flow where the dimensioneless shear rate $\dot\gamma=0.005$; The initial configuration is shown in panel (a). 
  }
    \label{figure6}
\end{figure}

Figures~\ref{figure5} and \ref{figure6} show two sets of simulations. Starting from the initial configuration (shown in both panel (a)), panels (b)-(d) show the transitions of two vesicles moving under an extensional flow. The extensional flow is stretching along the $y$ direction and squeezing in $x$ direction. Hence two vesicles are first pushed toward each other  then separate along the streamline. With the same starting state, panels (b)-(d) in Figure~\ref{figure6} are the observed phenomena when two vesicles are in a shear flow $\dot x = \dot\gamma y$. An interesting event occurs in the simulation that a rotational behavior with an adhesive effect can be observed and tuned. One can notice that the starting 
state of two vesicles are both centered on the x-axis. If two center of mass positions are not at the same horizontal level, then the adhesion observed in the shear flow case will be absent when they are well separated in $y$-direction.

@@

\begin{equation}
{\bf v}_\infty = v_{max}\left[ 1 - \left( \frac{y}{wR_0}\right)^2 \right]{\bf e}_x,
\end{equation}
%
where $v_{max}$ is the flow strength and $w$ controls the shape of the flow. $R_0$ is defined as the radius of the initial vesicle midplane. Figure~\ref{figure7} gives a final configuration for one specific case where the circular vesicle is initially placed above the $x$-axis.

\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{N58_parabolic.eps}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=20000$.
  }
    \label{figure7}
\end{figure}
